---
title: "Climate graphs generated with data from CDS - E-OBS datasets"
date: '2022-10-15'

execute:
  echo: false
---

## The times are changing..

We all are aware of how the climate is changing but to have a better feeling of it closer to home lets run some experiments.

Using climatology data grid from the CDS, mainly the data obtained in the dataset E-OBS, lets find out how has the weather changed aproximately over the last 50 years.

A little disclaimer; the data is an aproximation from the gridded data obtained , it should be close to reality but it wont be perfect. For that a lot of fine tuning of data would be necessary. I may get the AEMET on board to help me woth that :-).

Without more preamble here are the findings:

## Plottings

```{r}
#| label: plotting svg
#| warning: false
#| message: false

# Configuration
config <- yaml::read_yaml("params.yaml")

```

![](graphs/evaluate_2_cities_in_month.svg)

```{r}
#| label: plotting plotly 1
#| warning: false
#| message: false

# Configuration
config <- yaml::read_yaml("params.yaml")

readRDS(config$evaluate_2_cities_in_month$out$graph_r_obj_plotly)

```


![](graphs/evaluate_2_cities_in_month_1.svg)

```{r}
#| label: plotting plotly 2
#| warning: false
#| message: false

# Configuration
config <- yaml::read_yaml("params.yaml")

readRDS(config$evaluate_2_cities_in_month_1$out$graph_r_obj_plotly)

```



![](graphs/evaluate_decades_means.svg)


![](graphs/evaluate_decades_means_botton_10.svg)

